The language of generalization: Probability, vagueness, and interaction

### 2018-02-08 paper/comgen-paper.Rmd
edits to discussion

Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find certain people typing.
In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
This prediction can be described by a conditional probability: $p_{fk} = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ (formally, be in the set of things that have $f$) given that it is in $k$, which we will refer to as the **prevalence**.
The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
The properties also vary (e.g., having fur, causing jitters, typing). 
Yet the mathematical description of the inductive inference is always given by the probability $p_{fk}$.

How does one acquire such an inductive belief?
Observing instances of the category $k$ and noting how many of them have $f$ can support prediction to new instances when integrated with one's prior expectations about the property [cf., @Gelman2003; @Keil1992].
For example, if you observe creatures that \textsc{have two legs}, you might infer that all creatures of that category have two legs.
Observing new creatures with \textsc{broken wings}, however, leads to a much weaker prediction about other instances of the category having the property [@Nisbett1983].
This kind of domain-specific knowledge about properties can be represented formally as a probability distribution over the prevalence $p_{f}$: $P(p_{f})$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(p_{f} \mid d) \propto P(d \mid p_{f}) \cdot P(p_{f})$

@@

The language of generalization manifests when a property is predicated of a category: "Ks F" (e.g., "Dogs bark", "Staring at the sun makes you go blind"). 
Generalization from observations can be described as a predictive probability; it is intuitive then to posit that same quantity will be at the core of a semantic theory of the language of generalization.
To connect to the semantic tools of *truth values* [@Montague1973], we must relate the scalar quantity of probability to a Boolean value.
One simple way is with a *threshold semantics*: An utterance is true if the relevant quantity is above a threshold.
A threshold semantics for a generalization about category K with property F would then apply to the *prevalence* $p_{fk}$:
$\denote{K \text{ } F}(p_{fk}, \theta) = \{p_{fk} >\theta\}$

Various attempts of this kind have been made before [e.g., @Cohen1999].
We distinguish our proposal from previous ones by emphasizing the cognitive underpinnings of $p_{fk}$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.
$p_{fk}$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief.

@@

It is a remarkable fact that so much is learned from ideas expressed vaguely in words.
Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements---statements understood by even the youngest language users---can display complex sensitivities to context.
We have argued that the core meaning of such linguistic expressions is, in fact, simple, but underspecified. 
To our knowledge, this is the first formal theory of generalizations in language that makes precise quantitative predictions about human behavioral data.

As a formal theory of generalizations in language, we aim to unify significant swaths of language that are, on their surface, quite different from one another: generalizations about categories, events, and causes.
<!-- What these expressions have in common is *genericity*, the fact that these statements convey generalizations.  -->
We have been able to formalize a unified, core meaning using the underlying scale of *prevalence*.
We showed that all three kinds of generalizations exhibit the same kind of sensitivity to context (Expt. 1, 2a \& 2b, 3).
Our framework naturally accounts for a number of classic examples from the semantics of *generic language* (Expt. 1).
We provide an avenue for top-down moderators on language use, by elucidating the scale as defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
Finally, we have shown that listeners' prior knowledge about the prevalence of the feature in a category is causally related to their endorsement of statements of genericity (Expt. 3).
In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below

<!-- The theory we present here goes beyond previous accounts in a number of useful ways. -->
The foremost contribution of our theory is that it is accompanied by a formal model, which makes precise quantitative predictions about endorsments.
The formal Bayesian model provides a clean separation of the semantics of a generalization (operationalized in terms of the likelihood function) from background, world knowledge (operationalized in terms of the prior).
This formal separation is key improvement beyond previous accounts. 
Previous accounts have either tried to account for context-sensitivity by baking it into the semantics [e.g., @Cohen1999] or positing a semantics that cannot be separated from world knowledge [e.g., @Leslie2008].
Our model formalizes both the semantics of generalizations and the structure of world knowledge; this separation allows us to articulate a route for precise quantitative inlfuence of conceptual structure on generic language [c.f., @Leslie2008].
<!-- Our separation of world knowledge from the semantics of generics provides a substantial, but well-circumscribed role for conceptual structure to influence generic production and comprehension. -->
We do this without having to posit that conceptual structure and semantics are one in the same.
This is makes it possible to connect with theories of formal semantics as well as applied Natural Language technologies that seeks to draw inferences from information conveyed in generalizations in text [e.g., @Herbelot2011].
<!-- Statistical accounts in particular [@Cohen1999; @Nickel2008] -->

@@

In the rest of this discussion, we elaborate some key features of the theory that warrant future investigation, sketch out arguments for other known philosophical puzzles in genericity, and situate our theory with respect to extant theories of genericity.
<!-- We conclude by sketching out arguments for other known philosophical puzzles in genericity. -->

## A step towards communicating generalizations
<!-- Implicit aspects of language use: The comparison class and question under discussion -->

In this paper, we proposed a model for interpreting and endorsing generalizations in language by formalizing a simple semantic theory in a probabilistic model with structured, prior knowledge.
Our pair of models can be seen as a special case of a Rational Speech Act model, a rational framework of pragmatic language understanding [@Frank2012; @Goodman2016].
Our endorsement model, which we use to generate predictions for our three case studies, can be seen as a special case of a speaker model who can only produce one of two utterances: the generalization or silence. 
Our interpreter model can be seen as a kind of "literal listener", who does not do any sort of pragmatic or communicative reasoning. 
Our modeling framework could thus naturally be extended to more faithful models of pragamtic communication of generalizations, to explore when and how people choose to communicate their abstract knowledge when they have more options than in a two-alternative forced-choice task.
The view of our endorsement model as a minimal communicative model highlights aspects of our modeling approach for further future development.

### The comparison class

Our model of an interpreter, or naive listener, has access to implicit statistics of the event or property in question, represented by the prior belief distribution over the prevalence $P(h)$.
The prevalence priors for a property, event, or cause are constructed by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
Thus, the prevalence prior $P(h)$ is constructed with respect *the comparison class* $C$: $P_C(h)$.

The existence of comparison classes is uncontroversial in the study of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analagous to the context-sensitivity of the language of generalizations explored in this paper.
Thus, we conclude generic, habitual, and causal language can be seen as a special case of *vague language*.

The construction of a comparison class adds another layer of flexibility into the use of generalizations in language. 
Objects can be conceptualized and categorized in multiple ways, giving rise to multiple, logically-possible comparison classes (e.g., a robin is a bird, is an animal, is an object). 
We have begun doing work investigating how pragmatic reasoning can help constrain this open-ended problem [@Tessler2017].
Even if interlocutors coordinate on a particular comparison class, they may disagree about the prevalences for other *other categories* in the class.
That is, our model makes the prediction that the acceptance or rejection of the statement "Humans cause global warming" or "Muslims are terrorists" depends upon a speaker's beliefs about how *other forces* (e.g., plate tectonics) influence the climate or how often other social categories (e.g., neo-nazis) commit acts of terrorism.
Indeed, we saw in Expt. 3 how the statistics of other causes can influence the endorsement of a single generalization (e.g., "Herb C makes animals sleepy").
Understanding how knowledge of the comparison class influences language use is an exciting new area for future research in the language of generalizations.

### Question under discussion

Rational models of communication, of the kind we have developed in this paper, are required to make explicit a speaker's assumptions about the goal of communication, otherwise known as the Question Under Discussion or QUD [@roberts1996qud]. 
We have made a very minimalist assumption, that the goal of communication (at least, for purposes of endorsement) is the prevalence.
However, the choice in constructing a comparison class can be thought of as the result of addressing a particular QUD.
For example, the comparison classes used in our case studies were with respect to the target category (*other animals*, *other people*, *other possible causes*); thus, our model addresses the implicit QUDs of "*what* has feature?", "*who* does action?", or "*what* causes effect?".
Were the QUDs to be reversed (e.g., "what features does category have?", "what does person do?", "what effects does cause bring about?"), the comparison classes would need to be constructed with respect to the feature (e.g., *other features*, *other actions*, *other effects*).

The QUD is thus another layer of flexibility that makes understanding generalizations so challenging.
The same sentence can be used to address multiple QUDs [@KrifkaGenericBookFocus].
The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law."; imagine in a pedagogical context) or a feature-wise comparison class (i.e., "Lawyers care about the law *(as opposed to justice, doing what's morally right, ...)*" e.g., when said sardonically).
In this work, we focused on category-wise comparison classes for methodological convenience. 
<!-- In our three case studies, the *category-wise* comparison classes are fixed to *other people*, *other causes*, or *other kinds*, even as we vary the features. -->
<!-- *Feature-wise* comparison classes are likely to be modulated by the feature itself. -->
Future work should investigate the feature-wise reading of generalizations, and explore what cues listeners adopt for one or the other interpretation.

<!-- In the minimal contexts employed in our experiments, this is a reasonable assumption. -->
<!-- There is a different assumption we could have made, however: Another clear way to construct the comparison class is with respect to other features.  -->
<!-- This *feature-wise* comparison class would correspond to addressing the implicit QUDs: *what does \textsc{person} do?*, *what effects does \textsc{cause} bring about?*, and *what features does \textsc{kind} have?* -->

@@

@@

Previous psychological and philosophical work on generics has looked beyond prevalence and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].
Prasada has argued for a distinction between \emph{characteristic} properties (e.g., "Diapers are absorbent") and \emph{statistical} properties (e.g., "Diapers are white").
Leslie suggests information that is striking (e.g., "Tigers eat people") is ecologically useful and thus permitted to be a generic.
Gelman outlines how generics tend to express \emph{essential} qualities that are relatively timeless and enduring. 
Where in the probability-based semantics could such conceptual distinctions come into play?

Our approach makes the strong claim that beliefs about predicted prevalence are the connective tissue between conceptual knowledge and the semantics of generic language.
That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding prevalence distributions.
Modulations of prevalence distributions can occur for multiple reasons (e.g., by changing the comparison class) as described in the previous section.
We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to quantitatively different prevalence priors, even while keeping the comparison class fixed. 
In Expt. 3 we showed that these prevalence distributions are causally related to endorsement.

It is natural to ask how prevalence might reflect conceptual knowledge.
We found that empirical prevalence distributions are structured in a mixture-model that plausibly reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations. 
It is plausible that richer conceptual knowledge also influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992].
Indeed, conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately described via their impact on prevalence priors.

@@

This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
In previous accounts, prevalence is treated as synonymous with the frequency of the feature in the category. 
We make the important distinction that probability can be more general than frequency, and in our account, underlies speakers' subjective, predictions about the future and is subject to top-down moderator.
Expts. 2c \& 2d that showed using participants' \emph{predictions} about the future as the object of communication in our formal model perfectly tracked habitual endorsement, when the present frequency would make the wrong prediction.

Communicating probabilities might seem contrary to a basic tenet in cognitive psychology, that human cognition falls short when reasoning about probabilities [@Tversky1974].
Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the *language used* to convey *explicit probabilties* [cf., @Levinson1995]. 
Rather than conveying *explicit probabilities*, generalizations we argue convey *implicit probabilities*, which are easier to understand and quite useful for statistical reasoning.
Given the relationship to *vague language* (described above), we argue that the utterance "70% of birds fly" is analagous to saying that "John is 6'3"", while saying "Birds fly" is more similar to saying "John is tall".
The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
Indeed, young children are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to language [@Gweon2010; @Dewar2010].

@@

## Acquiring the language of generalizations

The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers.
Generic language is one of the earliest emerging forms of complex, compositional language.
Somewhere between two and three years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008].
Generics are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004],

What is perhaps surprising from a formal perspective is that generic language is far from trivial to characterize. 
If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...).
The extreme flexibility of generic meaning (e.g., "Birds lay eggs" vs. "Birds are female") stands in stark contrast to its early emergence in development.
In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015], and are often confused for generic statements [@Leslie2012a].
This has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is not approrpriate for generic language [@Leslie2008].

We think rejecting the normal tools of truth-functional semantics for generics would be throwing out the baby with the bathwater.
When we consider the acquisition problem, there are three aspects of meaning that a child must acquire for a truth-functional quantifier semantics $\denote{u}(h, \theta) = \{h :h > \theta\}$: 
(1) the dimension being described (i.e., the probability $h$),
(2) the polarity of the relation (i.e., $>$ vs. $<$), and 
(3) the value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
Upon learning the meaning has to do with probability and that it stands in a positive relation to some standard $\theta$, a rational learner would adopt a prior distribution over possible thresholds $\theta$, as a form of *lexical uncertainty* [@Bergen2016].
This prior could then be updated with more data to acquire a fixed meaning.
However, for the generic statement, the language learner is done once she acquires aspects (1) and (2).
In our model, $\theta$ is left underspecified in the semantics and is inferred in context.
Thus, in this sketch of an acquisition model, a child would first acquire generic language, and from that, carve out more precise meanings for quantified language.

The uniform prior over the threshold $\theta$ in the truth-functional threshold semantics (as we have assumed in our model) provides a secondary argument for why acquiring our semantics for generics should be easy.
Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the prevalence $h$ *itself*:

$$
\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h
$$
This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better the utterance", or simply "more is better") is perhaps the simplest semantics one could imagine.
The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
We leave for future work the precise implementation of the acquisition model we sketch out here.

@@

In our experiments, we have tried to include classic, philosophically puzzling examples of generalizations in language in addition to crafting novel stimuli that provide stricter tests of the main hypothesis.
In this section, we consider some other previously-discussed troubling examples of generalizations and sketch out arguments rooted in our theoretical framework to demonstrate how our theory could account for these cases. 
We consider the five following examples:

1. Books are paperbacks.
2. Mary handles the mail from Antarctica.
3. Supreme Court Justices have even social security numbers.
4. Elephants live in Africa and Asia.
5. Women are submissive.

>>>>

Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find people that we know doing what they habitually do. 
In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
This prediction can be described by a conditional probability: $p_{fk} = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the **prevalence**.
In particular, we define prevalence as a latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
The properties also vary (e.g., having fur, causing jitters, going to the gym).
Yet the mathematical description of the inductive belief is always given by a probability $p_{fk}$.

How does one acquire such an inductive belief?
If you observe creatures that *have two legs*, you might infer that all creatures of that kind have two legs.
But not all properties have such strong projectibility or prevalence.
Seeing a creature with *broken wings* tells you much less about other instances of the category having broken wings [@Nisbett1983].
This kind of domain-specific knowledge about properties can be represented formally as a probability distribution over the prevalence $p_{f}$: $P(p_{f})$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(p_{f} \mid d) \propto P(d \mid p_{f}) \cdot P(p_{f})$

@@

The language of generalization manifests when a property is predicated of a category: "Ks F" (e.g., "Dogs bark", "Staring at the sun makes you go blind"). 
Generalization from observations can be described as a predictive probability; it is intuitive then to posit that same quantity will be at the core of a semantic theory of the language of generalization.
To connect to the semantic tools of *truth values* [@Montague1973], we must relate the scalar quantity of probability to a Boolean value.
One simple way is with a *threshold semantics*: An utterance is true if the relevant quantity is above a threshold.
A threshold semantics for a generalization about category K with property F would then apply to the *prevalence* $p_{fk}$:
$\denote{K \text{ } F}(p_{fk}, \theta) = \{p_{fk} >\theta\}$
Various attempts of this kind have been made before [e.g., @Cohen1999].
We distinguish our proposal from previous ones by emphasizing the predictive nature of $p_{fk}$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.
<!-- $p_{fk}$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief. -->

@@

It is a remarkable fact that so much is learned from ideas expressed vaguely in words.
Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements---statements understood by even the youngest language users---can display complex sensitivities to context.
We have argued that the core meaning of such linguistic expressions is simple, but underspecified. 
To our knowledge, this is the first formal theory of generalizations in language that makes precise quantitative predictions about human behavioral data.

As a formal theory of generalizations in language, we aim to unify significant swaths of language that are, on their surface, quite distinct from one another: "Birds lay eggs", "Sally smokes", "Herb X makes animals sleepy".
<!-- What these expressions have in common is *genericity*, the fact that these statements convey generalizations.  -->
We have formalized a unified, core meaning using the underlying scale of predictive probability or *prevalence*.
We showed that all three kinds of generalizations exhibit the same kind of sensitivity to context (Expt. 1, 2a \& 2b, 3).
Our framework naturally accounts for a number of logically puzzling category generalizations, or *generics* (Expt. 1).
We provide an avenue for top-down moderators on language use, by elucidating the scale as defined by a subjective, predictive probability, not mere frequency (Expt. 2c).
Finally, we have shown that listeners' prior knowledge about the prevalence of the feature in a category is directly related to their endorsement of statements of genericity (Expt. 3).
<!-- In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below. -->

In this paper, we proposed a model for interpreting and endorsing generalizations in language by formalizing a simple semantic theory in a probabilistic model with structured, prior knowledge.
Our pair of models can be seen as a special case of a Rational Speech Act model, a rational framework of pragmatic language understanding [@Frank2012; @Goodman2016].
The endorsement model, which we use to generate predictions for our three case studies, is a special case of a speaker model who can only produce one of two utterances: the generalization or silence. 
The interpreter model is a "literal listener", who updates its beliefs by averaging over plausibly thresholds given prior knowledge and the simple truth-functional meaning.

<!-- The theory we present here goes beyond previous accounts in a number of useful ways. -->
<!-- The foremost contribution of our theory is that it is accompanied by a formal model, which makes precise quantitative predictions about endorsments. -->
The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization (operationalized in terms of the likelihood function) from background, world knowledge (the prior).
This formal separation is a key advancement beyond previous accounts, which have either aimed to account for context-sensitivity by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [e.g., @Leslie2008].
Our model formalizes a simple semantics for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data.
That is, we provide a route for precise quantitative influence of conceptual structure on generic language by way of shared background knowledge between speakers and listeners [c.f., @Leslie2008].
In the rest of this discussion, we elaborate some key features of the theory that warrant future investigation, sketch out arguments for other known philosophical puzzles in genericity, and situate our theory with respect to extant theories of genericity.

Our approach makes the strong claim that predictive probabilities are the connective tissue between conceptual knowledge and the semantics of generalizations.
That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding speaker beliefs or listener prevalence distributions, which can occur for multiple reasons (e.g., by changing the comparison class).
We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to quantitatively different prevalence priors, even while keeping the comparison class fixed. 
In Expt. 3 we showed that these prevalence distributions are causally related to endorsement.

<!-- Our separation of world knowledge from the semantics of generics provides a substantial, but well-circumscribed role for conceptual structure to influence generic production and comprehension. -->
<!-- We do this without having to posit that conceptual structure and semantics are one in the same. -->
<!-- This is makes it possible to connect with theories of formal semantics as well as applied Natural Language technologies that seeks to draw inferences from information conveyed in generalizations in text [e.g., @Herbelot2011]. -->
<!-- Statistical accounts in particular [@Cohen1999; @Nickel2008] -->

@@

<!-- We conclude by sketching out arguments for other known philosophical puzzles in genericity. -->

<!-- Implicit aspects of language use: The comparison class and question under discussion -->

<!-- to explore when and how people choose to communicate their abstract knowledge when they have more options than in a two-alternative forced-choice task. -->
<!-- The view of our endorsement model as a minimal communicative model highlights aspects of our modeling approach for further future development.  -->

## The comparison class

Our model of an interpreter, or naive listener, has access to implicit statistics of the event or property in question, represented by the prior belief distribution over the prevalence $P(h)$.
The prevalence priors for a property, event, or cause are constructed by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
Thus, the prevalence prior $P(h)$ is constructed with respect some comparison class $C$: $P_C(h)$.

The existence of comparison classes is uncontroversial in the study of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analagous to the context-sensitivity of the language of generalizations explored in this paper.
However, like the semantics of generalizations, the other entities or categories that comprise the comparison class are underspecified.

Uncertainty about the comparison class adds yet more flexibility to generalizations.
Even if interlocutors coordinate on a particular comparison class (e.g., agreeing that they are talking *relative to other animals*), they may disagree about the prevalences for other *other categories* in the class.
That is, our model makes the prediction that the acceptance or rejection of the statement "Humans cause global warming" or "Muslims are terrorists" depends upon a speaker's beliefs about how other forces (e.g., plate tectonics) influence the climate or how often other categories (e.g., neo-nazis) commit acts of terrorism.
In Expt. 3, we demonstrated the influence of other categories on endorsement of a generalization.
Understanding how knowledge of the comparison class influences language use is an exciting new area for future research in the language of generalizations.

Interlocturs may not only fail to coordinate on what categories are in the comparison class, the prevalences that may be assumed for the constituent categories of the comparison class, but *how* the comparison class should be constructed.
The comparison classes used in our case studies were with respect to the target *category* (*other animals*, *other people*, *other possible causes*); thus, our model addresses the implicit Question Under Discussion [QUD; @roberts1996qud] of "*what* has feature?".
Were the QUD to be reversed (e.g., "what features does category have?"), the comparison classes would need to be constructed with respect to the *feature* (e.g., *other features*, *other actions*, *other effects*).
The same sentence can be used to address multiple QUDs [@KrifkaGenericBookFocus], giving rise to multiple distinct comparison classes.
The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law."; imagine in a pedagogical context) or a feature-wise comparison class (i.e., "Lawyers care about the law *(as opposed to justice, doing what's morally right, ...)*" e.g., when said sardonically).
In this work, we focused on category-wise comparison classes for methodological convenience.
Future work should investigate the factors that give rise to feature-wise interpretations of generalizations, and how the relevant comparison classes are constructed.

<!-- Thus, we conclude generic, habitual, and causal language can be seen as a special case of *vague language*.  -->
<!-- The construction of a comparison class adds another layer of flexibility into the use of generalizations in language. -->
<!-- Objects can be conceptualized and categorized in multiple ways, giving rise to multiple, logically-possible comparison classes (e.g., a robin is a bird, is an animal, is an object).  -->
<!-- We have begun doing work investigating how pragmatic reasoning can help constrain this open-ended problem [@Tessler2017]. -->

<!-- ### Question under discussion -->

<!-- However, the choice in constructing a comparison class can be thought of as the result of addressing a particular QUD. -->
<!-- The QUD is thus another layer of flexibility that makes understanding generalizations so challenging. -->
<!-- In the minimal contexts employed in our experiments, this is a reasonable assumption. -->
<!-- There is a different assumption we could have made, however: Another clear way to construct the comparison class is with respect to other features.  -->
<!-- This *feature-wise* comparison class would correspond to addressing the implicit QUDs: *what does \textsc{person} do?*, *what effects does \textsc{cause} bring about?*, and *what features does \textsc{kind} have?* -->

@@

Rational models of communication, of the kind we have developed in this paper, make explicit a speaker's assumptions about the goals of communication, sometimes referred to as the Question Under Discussion or QUD [@roberts1996qud]. 
Our simple endorsement model assumes that the goal of communication is the prevalence.
This idealization will surely be elaborated in richer communicative contexts. 
It is noteworthy, however, when using a structured model of the prior (e.g., a mixture model), as we have used throughout this paper, that the endorsement model makes almost identical predictions if the QUD is assumed the more abstract parameters of the background knowledge (e.g., which mixture component the referent is part of).

@@

Previous psychological and philosophical work on generics has looked beyond prevalence and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].
Prasada has argued for a distinction between *characteristic* properties (e.g., "Diapers are absorbent") and *statistical* properties (e.g., "Diapers are white").
Leslie suggests information that is striking (e.g., "Tigers eat people") is ecologically useful and thus permitted to be a generalization, even if the property is not widespread.
Gelman outlines how generics tend to express *essential* qualities that are relatively timeless and enduring. 
Where in the probability-based semantics could such conceptual distinctions come into play?

We found that empirical prevalence distributions are best modeled as a mixture-model. 
Such a prior distribution draws qualitative distinctions (with respect to the feature) between different kinds of categories by virtue of the model representing multiple distinct components. 
It is likely that conceptual knowledge is far-richer than our simple two-component mixture-model, though a richer model of the prior is not necessary to account for the context-sensitive endorsement patterns we observe in our data. 
<!-- influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992]. -->
Indeed, conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
Future work will be needed to explore how probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately described via their impact on prevalence priors.

@@

This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
In previous accounts, prevalence is treated as synonymous with the frequency of the feature in the category. 
We make the distinction that what is communicated is probability not frequency.
Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
<!-- Expts. 2c \& 2d that showed using participants' *predictions* about the future as the object of communication in our formal model perfectly tracked habitual endorsement, when the present frequency would make the wrong prediction. -->

Communicating probabilities might seem contrary to a basic tenet in cognitive psychology, that human cognition falls short when reasoning about probability [@Tversky1974].
Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the language used to convey explicit probabilties [cf., @Levinson1995]. 
Rather than conveying *explicit probabilities*, generalizations we argue convey *implicit probabilities*, which are easier to understand and quite useful for statistical reasoning.
Given the relationship to *vague language* (described above), we argue that the utterance "70% of birds fly" is analagous to saying that "John is 6'3"", while saying "Birds fly" is more similar to saying "John is tall".
The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
Indeed, young children are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to the actual language of probability [@Gweon2010; @Dewar2010].

@@

## Acquiring the language of generalization

<!-- The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers. -->
<!-- Generic language is one of the earliest emerging forms of complex, compositional language. -->
<!-- Somewhere between two and three years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008]. -->

Perhaps the most surprising aspect of the language of generalization is how difficult it is to formalize, given how common they are in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004].
<!-- from a formal perspective is that generic language is far from trivial to characterize.  -->
<!-- Generalizations are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004], -->
Generalizations are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is in fact *easier* to formalize, but more difficult for young children to acquire [@Brandone2014; @Gelman2015].
<!-- If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...). -->
<!-- The extreme flexibility of generic meaning (e.g., "Birds lay eggs" vs. "Birds are female") stands in stark contrast to its early emergence in development. -->
<!-- In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015], and are often confused for generic statements [@Leslie2012a]. -->
This asymmetry between the simplicity of the formal theory and the age acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is inapprorpriate for generic language [@Leslie2008].

Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
The acquisition of a threshold-based truth-functional meaning $\denote{u}(h, \theta) = \{h :h > \theta\}$ requires learning at least three aspects of meaning: 
(1) the *dimension* being described (i.e., the probability $h$),
(2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
(3) the value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
Upon acquiring the dimension and the polarity, a rational learner should represent uncertainty over possible thresholds $\theta$.
Upon repeated cross-situational data, this prior could be updated towards acquiring a fixed meaning.
However, for generalizations, no fixed threshold is required; the language of generalization is acquired once aspects (1) and (2) are learned.
<!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
This informal analysis predicts that a child would first acquire generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data.

There is a secondary argument for why the semantics we posit presents an easy learning problem.
<!-- The uniform prior over the threshold $\theta$ in the truth-functional semantics (as we have assumed in our model) provides a secondary argument for why acquiring our semantics for generics should be easy. -->
Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function (as we have assumed in our model) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the degree, in this prevalence $h$ itself: $\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h$
This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better", or simply "more is better") is perhaps the simplest quantitative semantics one could posit.
The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
We leave for future work the precise implementation of the acquisition model we sketch out here.

@@

We aimed to balance two competing goals in designing our experimental stimuli: (1)  including familiar, philosophically puzzling examples that have been discussed in the vast literature on generic language and (2) introducing novel stimuli that provide targeted tests of our model.
In this section, we discuss how a few other previously-discussed troubling examples of generalizations could be addressed in our communicative framework.
We consider the five following examples:

1. Mary handles the mail from Antarctica.
2. Supreme Court Justices have even social security numbers.
3. Elephants live in Africa and Asia.
4. Books are paperbacks.
5. Women are submissive.
